Results_paper1

### 2019-05-02 Paper1_results.Rmd
daily_updated

library(tidyverse)
library(plyr)
library(lubridate)
library(ggpubr)
library(zoo)
library(lubridate)
library(FNN)
library(forecast)
library(astrochron)
library(WaveletComp)
library(data.table)
library(heatwaveR)
library(viridis)
library(ggrepel)
library(plyr)
library(maptools)
library(sp)
library(geosphere)
library(PBSmapping)
library(scales)
library(grid)
library(gridExtra)
library(circular)
library(fossil)
library(mapproj)
library(ncdf4)
library(reshape2)
library(plyr) # Never load plyr when also loading the tidyverse. It causes a lot of conflicts.
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(fasttime)
library(xtable)

@@

OISSTDir <- "~/Documents/Masters_2019/Data_SST"
OISST <- fread(paste0(OISSTDir, "/csvavhrr-only-v2-19810901-20180630.csv"),
            col.names = c("lon", "lat", "temp", "date"))

@@

```{r}
load("Data_P1/south_africa_coast.RData")
# load("Data_P1/bathy/sa_bathy.RData")
# load("Data_P1/bathy/bathy.RData")
load("Data_P1/site_list_sub.Rdata")
load("Data_P1/site_pixels.RData")
load("Data_P1/MUR.RData")
names(south_africa_coast)[1] <- "lon"

@@

@@

wind_UI <- insitu_wind %>%
          group_by(site) %>%
          mutate(ui.saws = mean_speed * (cos(dir_circ - 160)))

index <- wind_UI %>%
  group_by(site) %>% 
  select("site", "date","ui.saws") %>% 
  left_join(SACTN_fyears_UI, by = c("date", "site")) %>% 
  mutate(ws.condition = ifelse(ui.saws > 0, "upwelling", "downwelling"))

#Plotting the data
#SAWS data
ggplot(index, aes(x= date, y=ui.saws)) +
  geom_area(aes(fill=ws.condition)) +
  facet_wrap(~site) +
  geom_line() +
  geom_hline(yintercept=0)

# Visualisation
```

>>>>

library(tidyverse)
library(plyr)
library(lubridate)
library(ggpubr)
library(zoo)
library(lubridate)
library(FNN)
library(forecast)
library(astrochron)
library(WaveletComp)
library(data.table)
library(heatwaveR)
library(viridis)
library(ggrepel)
library(plyr)
library(maptools)
library(sp)
library(geosphere)
library(PBSmapping)
library(scales)
library(grid)
library(gridExtra)
library(circular)
library(fossil)
library(mapproj)
library(ncdf4)
library(reshape2)
library(plyr) # Never load plyr when also loading the tidyverse. It causes a lot of conflicts.
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(fasttime)
library(xtable)
library(ggpubr)

@@

```{r}
OISSTDir <- "~/Documents/Masters_2019/Data_SST"
OISST <- fread(paste0(OISSTDir, "/csvavhrr-only-v2-19810901-20180630.csv"),
            col.names = c("lon", "lat", "temp", "date"))

@@

```{r}
load("Data_P1/south_africa_coast.RData")
load("Data_P1/africa_coast.RData")
load("Data_P1/sa_provinces_new.RData")
# load("Data_P1/bathy/sa_bathy.RData")
# load("Data_P1/bathy/bathy.RData")
load("Data_P1/site_list_sub.Rdata")
load("Data_P1/site_pixels.RData")
load("Data_P1/MUR.RData")
names(south_africa_coast)[1] <- "lon"

@@

africa_map <- ggplot(africa_coast, aes(x = lon, y = lat)) + 
  theme_bw() + 
  coord_equal() + 
  geom_polygon(aes(group = group), colour = "black", fill = "grey80") + 
  geom_polygon(data = sa_provinces_new, (aes(group = group))) +
  annotate("text", label = "Africa", x = 16.0, y = 15.0, size = 3) + 
  theme(panel.border = element_rect(colour = "black", size = 0.4), 
        plot.background = element_blank(), 
        axis.ticks = element_blank(), 
        axis.text = element_blank(), 
        axis.title = element_blank(), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  coord_map(xlim = c(-20, 53), ylim = c(-36, 38), projection = "mercator") 
africa_map

# More mapping - http://r-nold.blogspot.com/2014/06/creating-inset-map-with-ggplot2.html

pdf("Figures/map_fixed.pdf", width = 8, height = 5, pointsize = 6) # Set PDF dimensions
vp1 <- viewport(x = 0.70, y = 0.58, w = 0.25, h = 0.25, just = c("left", "bottom")) # Africa
vp2 <- viewport(x = 1.0, y = 1.0, w = 1.00, h = 1.00, just = c("right", "top"))  # South Africa
print(site_map, vp = vp2)
print(africa_map, vp = vp1)
dev.off()

@@

wind_UI <- insitu_wind %>%
  group_by(site) %>%
  mutate(ui.saws = mean_speed * (cos(dir_circ - 160))) %>% 
  drop_na()

index <- wind_UI %>%
  group_by(site) %>% 
  select("site", "date","ui.saws") %>% 
  left_join(SACTN_fyears_UI, by = c("date", "site")) %>% 
  mutate(saws.condition = ifelse(ui.saws > 0, "upwelling", "downwelling"))

#Plotting the data
#SAWS data
ggplot(index, aes(x= date, y=ui.saws)) +
  geom_area(aes(fill=saws.condition)) +
  facet_wrap(~site) +
  geom_line() +
  geom_hline(yintercept=0)

index_SP <- index %>% 
  filter(site == "Sea Point") %>% 
  slice(-(c(34:70,435:632,686,1704)))

index_KOM <- index %>% 
  filter(site == "Kommetjie")

index_PN <- index %>% 
  filter(site == "Port Nolloth")

index_YZ <- index %>% 
  filter(site == "Yzerfontein")

index_LB <- index %>% 
  filter(site == "Lamberts Bay")

index_SB <- index %>% 
  filter(site == "Saldanha Bay")

# Visualisation
#Plotting the data
#SAWS data

upwell_plot <- function(df){
  plot <- df %>% 
  ggplot(aes(x= date, y=ui.saws)) +
  geom_area(aes(fill=saws.condition)) +
  geom_hline(yintercept=0)
}

upwell_SP <- upwell_plot(df = index_SP) 
upwell_KOM <- upwell_plot(df = index_KOM) 
upwell_PN <- upwell_plot(df = index_PN) 
upwell_YZ <- upwell_plot(df = index_YZ) 
upwell_SB <- upwell_plot(df = index_SB) 
upwell_LB <- upwell_plot(df = index_LB)

upwell_int <- function(df){
  interp <- approx(df$date, df$ui.saws, n=100000)
}
upwell_int_SP <- upwell_int(df = index_SP) 
upwell_int_KOM <- upwell_int(df = index_KOM) 
upwell_int_PN <- upwell_int(df = index_PN) 
upwell_int_YZ <- upwell_int(df = index_YZ) 
upwell_int_LB <- upwell_int(df = index_LB) 
upwell_int_SB<- upwell_int(df = index_SB)

interp <- function(df){
  interp <- approx(df$date, df$ui.saws, n=100000)
}
interp_SP <- interp(df = index_SP) 
interp_KOM <- interp(df = index_KOM) 
interp_PN <- interp(df = index_PN) 
interp_YZ <- interp(df = index_YZ) 
interp_LB <- interp(df = index_LB) 
interp_SB<- interp(df = index_SB)

interp2 <- function(df){
  interp2 <- approx(df$date, df$ui.saws, n=100000)
}

interp2_SP <- interp2(df = index_SP) 
interp2_KOM <- interp2(df = index_KOM) 
interp2_PN <- interp2(df = index_PN) 
interp2_YZ <- interp2(df = index_YZ) 
interp2_LB <- interp2(df = index_LB) 
interp2_SB<- interp2(df = index_SB)

# Sea Point
UIi_SP <- data.frame(Day=interp_SP$x, Index=interp_SP$y, Temp = interp2_SP$y)
UIi_SP$saws_condition[UIi_SP$Index >= 0] <- "upwelling"
UIi_SP$saws_condition[UIi_SP$Index < 0] <- "downwelling"

index_plot_SP <- ggplot(UIi_SP, aes(x=Day, y=Index)) +
  geom_area(aes(fill=saws_condition)) +
  geom_hline(yintercept=0) +
  theme_bw() +
  # annotate("text", x = 300, y = -12.5, label = "SAWS Data") +
  #geom_vline(xintercept = c(116, 117, 133, 134, 244, 291), lty = 2, lwd = 1) +
  scale_fill_manual(values=c("salmon", "steelblue")) +
  scale_x_continuous(expand=c(0, 0)) +
  scale_y_reverse() +
  labs(y= "Upwelling Index") +
  guides(fill=guide_legend(title="Condition")) +
  ggtitle("Sea Point")
index_plot_SP

# Kom
UIi_KOM <- data.frame(Day=interp_KOM$x, Index=interp_KOM$y, Temp = interp2_KOM$y)
UIi_KOM$saws_condition[UIi_KOM$Index >= 0] <- "upwelling"
UIi_KOM$saws_condition[UIi_KOM$Index < 0] <- "downwelling"

index_plot_KOM <- ggplot(UIi_KOM, aes(x=Day, y=Index)) +
  geom_area(aes(fill=saws_condition)) +
  geom_hline(yintercept=0) +
  theme_bw() +
  # annotate("text", x = 300, y = -12.5, label = "SAWS Data") +
  #geom_vline(xintercept = c(116, 117, 133, 134, 244, 291), lty = 2, lwd = 1) +
  scale_fill_manual(values=c("salmon", "steelblue")) +
  scale_x_continuous(expand=c(0, 0)) +
  scale_y_reverse() +
  labs(y= "Upwelling Index") +
  guides(fill=guide_legend(title="Condition")) +
  ggtitle("Kommetjie")
index_plot_KOM

# Port Nolloth
UIi_PN <- data.frame(Day=interp_PN$x, Index=interp_PN$y, Temp = interp2_PN$y)
UIi_PN$saws_condition[UIi_PN$Index >= 0] <- "upwelling"
UIi_PN$saws_condition[UIi_PN$Index < 0] <- "downwelling"

index_plot_PN<- ggplot(UIi_PN, aes(x=Day, y=Index)) +
  geom_area(aes(fill=saws_condition)) +
  geom_hline(yintercept=0) +
  theme_bw() +
  # annotate("text", x = 300, y = -12.5, label = "SAWS Data") +
  #geom_vline(xintercept = c(116, 117, 133, 134, 244, 291), lty = 2, lwd = 1) +
  scale_fill_manual(values=c("salmon", "steelblue")) +
  scale_x_continuous(expand=c(0, 0)) +
  scale_y_reverse() +
  labs(y= "Upwelling Index") +
  guides(fill=guide_legend(title="Condition")) +
  ggtitle("Port Nolloth")
index_plot_PN

# Yzerfontein
UIi_YZ <- data.frame(Day=interp_YZ$x, Index=interp_YZ$y, Temp = interp2_YZ$y)
UIi_YZ$saws_condition[UIi_YZ$Index >= 0] <- "upwelling"
UIi_YZ$saws_condition[UIi_YZ$Index < 0] <- "downwelling"

index_plot_YZ<- ggplot(UIi_YZ, aes(x=Day, y=Index)) +
  geom_area(aes(fill=saws_condition)) +
  geom_hline(yintercept=0) +
  theme_bw() +
  # annotate("text", x = 300, y = -12.5, label = "SAWS Data") +
  #geom_vline(xintercept = c(116, 117, 133, 134, 244, 291), lty = 2, lwd = 1) +
  scale_fill_manual(values=c("salmon", "steelblue")) +
  scale_x_continuous(expand=c(0, 0)) +
  scale_y_reverse() +
  labs(y= "Upwelling Index") +
  guides(fill=guide_legend(title="Condition")) +
  ggtitle("Yzerfontein")
index_plot_YZ

# Lamberts Bay
UIi_LB <- data.frame(Day=interp_LB$x, Index=interp_LB$y, Temp = interp2_LB$y)
UIi_LB$saws_condition[UIi_LB$Index >= 0] <- "upwelling"
UIi_LB$saws_condition[UIi_LB$Index < 0] <- "downwelling"

index_plot_LB<- ggplot(UIi_LB, aes(x=Day, y=Index)) +
  geom_area(aes(fill=saws_condition)) +
  geom_hline(yintercept=0) +
  theme_bw() +
  # annotate("text", x = 300, y = -12.5, label = "SAWS Data") +
  #geom_vline(xintercept = c(116, 117, 133, 134, 244, 291), lty = 2, lwd = 1) +
  scale_fill_manual(values=c("salmon", "steelblue")) +
  scale_x_continuous(expand=c(0, 0)) +
  scale_y_reverse() +
  labs(y= "Upwelling Index") +
  guides(fill=guide_legend(title="Condition")) +
  ggtitle("Lamberts Bay")
index_plot_LB

# Saldanha Bay
UIi_SB <- data.frame(Day=interp_SB$x, Index=interp_SB$y, Temp = interp2_SB$y)
UIi_SB$saws_condition[UIi_SB$Index >= 0] <- "upwelling"
UIi_SB$saws_condition[UIi_SB$Index < 0] <- "downwelling"

index_plot_SB<- ggplot(UIi_SB, aes(x=Day, y=Index)) +
  geom_area(aes(fill=saws_condition)) +
  geom_hline(yintercept=0) +
  theme_bw() +
  # annotate("text", x = 300, y = -12.5, label = "SAWS Data") +
  #geom_vline(xintercept = c(116, 117, 133, 134, 244, 291), lty = 2, lwd = 1) +
  scale_fill_manual(values=c("salmon", "steelblue")) +
  scale_x_continuous(expand=c(0, 0)) +
  scale_y_reverse() +
  labs(y= "Upwelling Index") +
  guides(fill=guide_legend(title="Condition")) +
  ggtitle("Saldanha Bay")
index_plot_SB

upwelling_index <- ggarrange(index_plot_SP, index_plot_KOM, index_plot_PN,
          index_plot_YZ,index_plot_LB, index_plot_SB, ncol = 2, nrow = 3)
```
